\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-17 trunk/europa.tex
europ+concepts touch ups with Javier, fig for arch and updates to arch

\comment{provide snapshot of resource envelopes generated by europa}

@@

\item Open Condition: an open condition is an inactive token. Inactive
  tokens can be generated by explicitly posted goals, or when a token
  is activated, rules may fire that create inactive slave tokens
  \comment{point to more detailed decription above in Rules Engine
    section}.  Open Conditions can be resolved in three ways:

>>>>

\comment{figure :provide snapshot of resource envelopes generated by europa}

@@

\item Open Condition: an open condition is an inactive token. Inactive
  tokens can be generated by explicitly posted goals, or when a token
  is activated, rules may fire that create inactive slave tokens
  \comment{reference: point to more detailed decription above in Rules Engine
    section}.  Open Conditions can be resolved in three ways:
